\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{lmodern}
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}
%%
\usepackage{mdframed,xcolor}
%constant value%
\mdfdefinestyle{ProjectFrame}{%
	% linecolor=black,
%	outerlinewidth=2pt,
	%roundcorner=20pt,
	innertopmargin=0.1cm,
	innerbottommargin=0.1cm,
	innerrightmargin=0.1cm,
	innerleftmargin=0.1cm,
	leftmargin = 0.6cm,
	rightmargin = 0.2cm,
	linecolor=white,
	backgroundcolor=gray!5!white
	}

%%
\name{Khuong}{Nguyen Bao} 
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-13mm}
\begin{center}\textbf{ Software Developer - Corebanking Technical Solution DevOps }\end{center}
\begin{center}
\begin{tabular}{ c c c }
\quad\faMobile\enskip +84 919922081 & 
\quad\faEnvelope\enskip nbkhuong97@gmail.com & 
\quad\faHome\enskip Ho Chi Minh City, Vietnam \\
\faLinkedin\enskip\color{blue}\href{https://www.linkedin.com/in/khuong-nguyen76/}{in/khuong-nguyen76} &
\quad\faGithub\enskip\color{blue}\href{https://github.com/delvk}{github.com/delvk} & \faGitlab\enspace \color{blue} \href{https://gitlab.com/delvk}{gitlab.com/delvk}
\end{tabular}
\end{center}

\section{Profile}
{Results-oriented software engineer with 4+ years of experience specializing in core banking systems. Proven ability to design, develop, and implement complex solutions for Account, Deposit, and General Ledger modules. Expertise in Oracle, PL/SQL, and REST APIs. Strong background in DevOps practices, ensuring seamless integration and efficient operation of core banking applications.}

\section{Areas of Expertise}
{Corebanking Developer - Corebanking Integration - Financial Technical Solution - Data Analysis - Software Developer - Oracle - PLSQL - REST Api - Golang developer - Database Management - Development and Operation - Automation Testing - Microservices}

\section{Professional Experience}
\customcventry{11/2021 ‐ present}{{\color{blue}\href{https://www.vib.com.vn}{(Vietnam Int. Bank)}}}{Deposit, Payroll Solution DevOps Specialist,}{Dist.1, HCM City}{}{
\vspace*{2mm}
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Developed and operated technology solutions for Accounts, Deposits, Payroll.
\item Designed and developed integration flows and APIs between Core Banking and satellite systems (Mobile app, Counter App, etc.).
\item Developed new features and products for Core Banking.
\item Monitored operations, analyzed, and resolved errors arising in the Core Banking system.
\item[] \textbf{Technologies}: Oracle Forms and Reports, Oracle PLSQL, RESTful API.
\end{itemize}}}

\begin{mdframed}[style=ProjectFrame]
	\textbf{Project:} Cash Management \\
	\textbf{Time:} 11/2021 - 03/2023 \\
	\textbf{Description:} Bringing Branch Teller functions from the legacy system to the new system that the Bank developed itself\\
	\textbf{Responsibilities:}
	\begin{itemize}[leftmargin=0.6cm,noitemsep,topsep=0pt,label=-]
	\item Design, dev open/close daily flow for branches of the new system.
	\item Design, develop core integration APIs (transfer, collect fees, get GL information, transaction information, etc.)
	\item Consult, support operation.
	\end{itemize}
\end{mdframed}

%%TD investment
\begin{mdframed}[style=ProjectFrame]
	\textbf{Project:} TD Investment \\
	\textbf{Time:} 12/2021 - 07/2022 \\
	\textbf{Description:} Create a market for retail customers to transfer savings books.\\
	\textbf{Responsibilities:}
	\begin{itemize}[leftmargin=0.6cm,noitemsep,topsep=0pt,label=-]
		\item Designed and developed core integration APIs (account opening, account hold, fund hold, transfer, fee collection, information retrieval, etc.).
		\item Served as the technical lead for integration flow.
		\item Managed product operations.
	\end{itemize}
\end{mdframed}

%%TD Tradding
\begin{mdframed}[style=ProjectFrame]
	\textbf{Project:} TD Tradding\\
	\textbf{Time:} 02/2023 - 10/2023 \\
	\textbf{Description:} Mobilize capital from long-term deposits of corporate customers, through these organizations to sell smaller term books to industrial customers.\\
	\textbf{Responsibilities:}
	\begin{itemize}[leftmargin=0.6cm,noitemsep,topsep=0pt,label=-]
		\item Designed and developed integration APIs.
		\item Designed and developed the product's operational flow and jobs.
		\item Managed product operations.
	\end{itemize}
\end{mdframed}

%% Corebanking Transformation
\begin{mdframed}[style=ProjectFrame]
	\textbf{Project:} Corebanking transfomation \\
	\textbf{Time:} 11/2023 - Present \\
	\textbf{Description:} Upgrade corebanking to meet modern requirements such as performance, cloud integration, and its own integration module.\\
	\textbf{Responsibilities:} 
	\begin{itemize}[leftmargin=0.6cm,noitemsep,topsep=0pt,label=-]
		\item Responsible for integration documentation and integration flow for Account and Deposit modules.
		\item Responsible for data migration flow for Account and Deposit modules.
	\end{itemize}
\end{mdframed}

%% LienViet
%\customcventry{10/2021}{{\color{blue}\href{https://lpbank.com.vn}{(LienViet Post Bank)}}}{Reporting Dev., Data Analyst,}{Quận 1, Tp. HCM}{}{
	%{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			%\item Phát triển các báo cáo dùng oracle bi publisher trong Datawarehouse (PLSQL).
			%\end{itemize}}}
			
%% Eximbank
\customcventry{03/2020 - 09/2021}{{\color{blue}\href{https://eximbank.com.vn}{(Eximbank)}}}{Corebanking Developer,}{Dist.3, Ho Chi Minh City}{}
{
	\vspace*{2mm}
	\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
	\item Designed, developed, and operated Core Banking screens, functions, and APIs for General Ledger (GL), Details Ledger (DL), and Trade Finance (TF) modules.
	\item Developed and optimized reports and ETL scripts for responsible subsystems.
	\item[] \textbf{Technologies:} Oracle PLSQL, Infosys Script, Jasper Reports.
	\end{itemize}
}
 
%% HUB
\begin{mdframed}[style=ProjectFrame]
	\textbf{Project:}
	\begin{itemize}[leftmargin=0.6cm,noitemsep,topsep=0pt,label=-]
		\item Centralized Funding, One-Stop Teller
		\item Upgrade CITAD message to v2.5
	\end{itemize}
\end{mdframed}

\section{Certifications}
{\begin{itemize}[label={\textbullet}]
      \item Microsoft Certified: Azure Fundamentals (07/2022) - \underline{\color{blue}\href{https://drive.google.com/file/d/1qxYfcd0UYsWdJNqyOZ2rfYVV3GqyhA4x/view?usp=sharing}{AZ-900}}
      \item Toeic Listening \& Reading Certified: 905 (04/2019) - \underline{\color{blue}\href{https://drive.google.com/file/d/1RHzD2srmD5mtvXiPQpjvhY7--DFvFiKc/view?usp=sharing}{TOEIC}}
      \item Cisco Certified Network Associate (01/1999) - \underline{\color{blue}\href{https://google.com/}{CCNA}}
  \end{itemize}} 

\section{Education}
\customcventry{09/2015 - 03/2020}{\color{blue}\href{https://hcmut.edu.vn/}{HCM City University of Technology (HCMUT)}}{Computer Engineering}{Dist.10, HCM City}{}{}{Relevant Courses: Data Structure \& Algorithm, Computer Architecture, Programming Techniques, Database Systems, Computer Networks, Cryptography \& Network Security,...}
\section{Technical Skills}
\section{Technical Skills}
{\begin{itemize}[label={\textbullet}]
		\item \textbf{Languages}: PL/SQL, Golang, JavaScript, C/C++, Batch, Shell, Python, Java
		\item \textbf{Databases}: Oracle, PostgreSQL, MongoDB
		\item \textbf{Tools}: Git, ELK, Docker, Jmeter, Postman, Wireshark, Nmap, Toad, PL/SQL Developer, VSCode, WinSCP, Putty, Jenkins, Jira, Trello, EASparx
		\item \textbf{Microservices}: ELK, Kafka, WSO2 API Manager, WSO2 Identity Server
\end{itemize}}

\section{Languages}
\begin{multicols}{2}
    \begin{itemize}[label=\textbullet]
    \item \textbf{Vietnamese} [Native]
	\item {\textbf{English} [Basic] - Communication}
	\item {\textbf{English} [Advance] - Technical Document Reading}
    \end{itemize}
\end{multicols}
\end{document}